---
author: Yash Dhore
date: 2/21/2015
---

Executive Summary
========================================================

There is a set of variables related to miles per gallon (MPG) (dependent variable).

Here the difference of the MPG between automatic and manual transmissions is focused, the mtcars dataset in car package is taken as the data source, and techniques about regression models is used to solve the following two questions:

- Is an automatic or manual transmission better for MPG?
- Quantifying how different is the MPG between automatic and manual transmissions?

Load and Test Data
========================================================
The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973-74 models).


```{r}
library(datasets)
mpgData <- with(mtcars, data.frame(mpg, am))
mpgData$am <- factor(mpgData$am, labels = c("Automatic", "Manual"))

```

Q1: Is an automatic or manual transmission better for MPG?
========================================================

Comparing at the mean mpg, you can deduce that the manual transmission.

```{r, echo=TRUE}
summary(mpgData[mpgData$am == "Automatic",])
summary(mpgData[mpgData$am == "Manual",])
```

Q2: Quantifying how different is the MPG between automatic and manual transmissions?
====================================================================================

Let us build a simple linear model. It shows that manual transmission is better by 7.245 mpg.

```{r, echo=TRUE}
fit <- lm(mpg ~ as.integer(am), data=mpgData)
summary(fit)
```

Appendix: MPG between automatic and manual transmission
=======================================================

```{r, echo=TRUE}
par(mfrow=c(1,2))
with(mpgData,{
     boxplot(mpg ~ am, 
             ylab = "miles per gallon (MPG)")
     plot(mpg ~ as.integer(am),
             xlab = "Automatic (1) or Manual(2)",
             ylab = "miles per gallon (MPG)")
     abline(fit, col=2)
     })
```

